---
title: "HW 2 - Airbnb"
author: "Annie Hou"
date: "02/07/2024"
output: html_document
---

## Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
airbnb <- read_csv("data/airbnb.csv")
```

## Exercises

### Exercise 1

There are 13245 rows in the dataset.

### Exercise 2

Each row represents the information of an airbnb, including an id, price, neighborhood, accomodates, number of rooms and beds, ratings and score, and so on.

### Exercise 3

Remove this text, and add your answer for Exercise 3 here.

```{r prices-neighbourhoods}
# remove this comment and add the code for Exercise 3 here
```

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

```{r top-5-median}
# remove this comment and add the code for Exercise 4 here
```

```{r top-5-median-plot}
# remove this comment and add the code for Exercise 4 here
```

```{r top-5-median-summary-stats}
# remove this comment and add the code for Exercise 4 here
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

```{r review-scores-rating}
# remove this comment and add the code for Exercise 5 here
```
